Low-Cost Data Deduplication for Virtual Machine Backup in Cloud Storage

### 2013-05-14 hotstorage13/main.tex
save some lines
update acknowledgement

{\bf Acknowledgment.} We thank the anonymous referees for their valuable comments.
This work is supported in part by NSF IIS-1118106. 
Any opinions, findings, conclusions or recommendations expressed in this material
are those of the authors and
do not necessarily reflect the views of the National Science Foundation.

>>>>

{\bf Acknowledgment.} 
We wish to thank the following people for their contributions to the paper.
Renu Tewari (our shepherd) and the anonymous referees for their valuable comments. Michael Agun 
commented on the earlier drafts of the paper.
This work is supported in part by NSF IIS-1118106. 
Any opinions, findings, conclusions or recommendations expressed in this material
are those of the authors and
do not necessarily reflect the views of the National Science Foundation.
